---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/coatless/ucidata.svg?branch=master)](https://travis-ci.org/coatless/ucidata)[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/ucidata)](http://www.r-pkg.org/pkg/ucidata) [![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/ucidata)](https://cran.r-project.org/package=ucidata)

# `ucidata` - Data Sets from UC Irving's ML Library 

The following is an _R_ data package that features certain data sets from 
the [Machine Learning Library at UC Irving](https://archive.ics.uci.edu/ml/) 
These data sets have been cleaned up and provide documentation via _R_'s help system. 

## Installation

You can install `ucidata` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("coatless/ucidata")
```

## Using data in the package

There are two ways to access the data contained within this package. 

The first is to load the package itself and type the name of a data set.
This approach takes advantage of _R_'s lazy loading mechansim, which avoids
loading the data until it is used in _R_ session. For details on 
how lazy loading works, please see [Section 1.17: Lazy Loading](https://cran.r-project.org/doc/manuals/r-release/R-ints.html#Lazy-loading)
of the [R Internals](https://cran.r-project.org/doc/manuals/r-release/R-ints.html)
manual.

```{r use-data-package, eval = FALSE}
# Load the `ucidata` package
library("ucidata")

# See the first 10 observations of the `autompg` dataset
head(autompg)

# View the help documentation for `autompg`
?autompg
```

The second approach is to use the `data()` command to load data on the 
fly without and type the name of a data set.

```{r use-data-call, eval = FALSE}
# Loading `autompg` without a `library(ucidata)` call
data("autompg", package = "ucidata")

# See the first 10 observations of the `autompg` dataset
head(autompg)

# View the help documentation for `autompg`
?autompg
```

## Included Data Sets

The following data sets are included in the `ucidata` package:

- [`abalone`](https://archive.ics.uci.edu/ml/datasets/abalone)
- [`adult`](https://archive.ics.uci.edu/ml/datasets/adult)
- [`autoimports`](https://archive.ics.uci.edu/ml/datasets/Automobile)
- [`autompg`](https://archive.ics.uci.edu/ml/datasets/auto+mpg)
- Breast Cancer Wisconsin:
    - [`bcw_original` (Breast Cancer Wisconsin Original)](https://archive.ics.uci.edu/ml/datasets/bike+sharing+dataset)
- [`bike_sharing_daily`](https://archive.ics.uci.edu/ml/datasets/bike+sharing+dataset)
- [`bridges`](https://archive.ics.uci.edu/ml/datasets/Pittsburgh+Bridges)
- [`hepatitis`](https://archive.ics.uci.edu/ml/datasets/hepatitis)
- [`wine`](https://archive.ics.uci.edu/ml/datasets/wine)

## Build Scripts

Want to see how each data set was imported? Check out the [`data-raw`](https://github.com/coatless/ucidata/tree/master/data-raw) folder!
