---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/coatless/ucidata.svg?branch=master)](https://travis-ci.org/coatless/ucidata)[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/ucidata)](http://www.r-pkg.org/pkg/ucidata) [![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/ucidata)](https://cran.r-project.org/package=ucidata)

# `ucidata` - Datasets from UC Irving's ML Library 

The following is an _R_ data package that features certain data sets from 
the [Machine Learning Library at UC Irving](https://archive.ics.uci.edu/ml/) 
These data sets have been cleaned up and provide documentation via _R_'s help system. 

## Installation

You can install ucidata from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("coatless/ucidata")
```

## Included Data Sets

The following data sets are included in the `ucidata` package:

- [`wine`](https://archive.ics.uci.edu/ml/datasets/wine)
- [`autompg`](https://archive.ics.uci.edu/ml/datasets/auto+mpg)

## Build Scripts

Want to see how each data set was imported? Check out the [`data-raw`](https://github.com/coatless/ucidata/tree/master/data-raw) folder!
